A systematic search for transiting planets using \KT

### 2015-02-06 ms.tex
Words throughout.

The \kepler\ Mission (cite something) has been incredibly succesful at
finding periodic transits (eclipses) in the light curves (time-series
photometry) of stars.
Many of its most important discoveries are long-period planets that
make transits with tiny amplitudes and short durations.
The Mission has demonstrated that it is possible to routinely measure
signals in stellar light curves at the part-in-$10^5$ level, at least
for quiet and apparently bright stars.

@@

The \KT\ Mission (cite something) is a follow-on to the primary
\kepler\ Mission.
The primary mission came to an end with the failure of a critical
reaction wheel, rendering the spacecraft less able to maintain precise
pointing.
Because of the degraded spacecraft orientation systems, the new
\KT\ data will in general exhibit far greater pointing
variations---and far greater pointing-induced variations in
photometry---than the original \kepler\ data.
This makes good data-analysis techniques all the more valuable.

@@

The starting point for analysis is the raw pixel data.
We download the full set of XXX target pixel files for \KT's Campaign 1 from
MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
Then, we extract photometry using fixed circular apertures of varying sizes
centered on the mean position of the brightest star (on average) in each
frame.
The centroids and initial flux estimates were measured using
\project{simplexy}, a component of the \project{Astrometry.net} pipeline
\citep{astrometry}.
For each time series, we used 20 circular apertures ranging in radius from 0.5
to 10 pixels and---following \citet{vanderberg-a}---chose the aperture size
that resulted in the smallest CDPP \dfmtodo{CITE CDPP} with a 6 hour
window.\footnote{Note that although we chose a specific aperture, photometry
for every aperture size is available online at \dfmtodo{some URL}.}

@@

To use our distributions to characterize individual systems, one

>>>>

The \kepler\ Mission (cite something) has been incredibly succesful at
finding periodic transits (eclipses) in the light curves (time-series
photometry) of stars.
Many of its most important discoveries are long-period planets that
make transits with tiny amplitudes and short durations relative to the
planet's orbital period.
The Mission has demonstrated that it is possible to routinely measure
signals in stellar light curves at the part-in-$10^5$ level, at least
for quiet and apparently bright stars.

@@

The \KT\ Mission (cite something-Howell 14) is a follow-on to the primary
\kepler\ Mission.
The primary mission came to an end with the failure of a critical
reaction wheel, rendering the spacecraft less able to maintain precise
pointing.
Because of the degraded spacecraft orientation systems, the new
\KT\ data will in general exhibit far greater pointing
variations---and far greater pointing-induced variations in
photometry---than the original \kepler\ data.
This makes good data-analysis techniques all the more valuable.

@@

The starting point for analysis is the raw pixel data.
We download the full set of XXX target pixel files for \KT's Campaign 1 from
MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
Then, we extract photometry using fixed circular apertures of varying sizes
centered on the mean position of the brightest star (on average) in each
frame.
The centroids and initial flux estimates were measured using
\project{simplexy}, a component of the \project{Astrometry.net} pipeline
\citep{astrometry}.
For each time series, we used 20 circular apertures ranging in radius from 0.5
to 10 pixels and---following \citet{vanderberg-a}---chose the aperture size
that resulted in the smallest CDPP \dfmtodo{CITE CDPP-Jessie Christiansen,
Jon Jenkins, et al 2012} with a 6 hour
window.\footnote{Note that although we chose a specific aperture, photometry
for every aperture size is available online at \dfmtodo{some URL}.}

@@

To use these distributions to characterize the properties of specific systems,
one should weight our samples by inferred stellar properties.
